Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-24 paper/paper.tex
pass table iv

\setlength{\tabcolsep}{8pt}
\begin{table}[h!]
  \footnotesize
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    2100384 & 2 & \Fix{} & 2 & 2 & 2 \\
    2100399 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100401 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100402 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100408 & 2 & \Fix{} & 2 & 2 & 2 \\
    2100485 & 1 & \Fix{} & 1 & 1 & 1 \\
    2100486 & 1 & \Fix{} & 1 & 1 & 1 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 4 & 4 & 2\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 87 & 87 & 15\cellcolor{lightgray}$\downarrow$ & 84 & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 17 & 17 & 144$\uparrow$ & 27$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 1 & 1 & 15$\uparrow$ \\
    /system32/ in URI & 2  & 2 & 6$\uparrow$ & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$\\
    Basebuilder LFI & 48  & 48 & 846$\uparrow$ & 65$\uparrow$ & 664$\uparrow$\\
    Tomcat Snoop Access & 37  & 37 & 1797$\uparrow$ & 6\cellcolor{lightgray}$\downarrow$ & 3580$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\setlength{\tabcolsep}{8pt}
\begin{table}[h!]
  \footnotesize
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
    2100384 & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    2100399 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    2100401 & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    2100402 & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    2100408 & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    2100485 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    2100486 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    %%UDP Flood & - & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 4 & 4 & 2\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 87 & 87 & 15\cellcolor{lightgray}$\downarrow$ & 84 & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 17 & 17 & 144$\uparrow$ & 27$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 1 & 1 & 15$\uparrow$ \\
    /system32/ in URI & 2  & 2 & 6$\uparrow$ & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$\\
    Basebuilder LFI & 48  & 48 & 846$\uparrow$ & 65$\uparrow$ & 664$\uparrow$\\
    Tomcat Snoop Access & 37  & 37 & 1797$\uparrow$ & 6\cellcolor{lightgray}$\downarrow$ & 3580$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}
